---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {dehex}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R-CMD-check](https://github.com/matt-dray/dehex/workflows/R-CMD-check/badge.svg)](https://github.com/matt-dray/dehex/actions)
[![Codecov test coverage](https://codecov.io/gh/matt-dray/dehex/branch/main/graph/badge.svg)](https://codecov.io/gh/matt-dray/dehex?branch=main)
<!-- badges: end -->

'Dehex', from [Wiktionary](https://en.wiktionary.org/wiki/dehex):

> To remove a hex (a spell, especially an evil spell).

An R package containing simple functions to help me train myself to quickly 'read' a colour from its hex code. I'm colourblind (a deuteranope) so this might be a useful skill.

⚠ The package is very much a work-in-progress and things may change or break at any time.

The package functions follow the five steps in [David DeSandro's dotCSS 2018 talk](https://metafizzy.co/blog/read-color-hex-codes/) ([thanks Maëlle](https://twitter.com/ma_salmon/status/1420726230194794496?s=20)):

1. Simplify the hex code
1. Create a bar chart
1. Assess hue from graph 'shape'
1. Assess lightness from total
1. Assess saturation from range

Install the development version from GitHub with:
 
```{r install, eval=FALSE}
remotes::install_github("matt-dray/dehex")
```

First, convert a full six-character hex code to its three-character shortcode:

```{r ex-shorten}
long <- "#E22A31"
short <- dehex::dh_shorten(long)
short
```

Then print a bar chart to your console that describes the relative amounts of red, green and blue described by the shortcode:

```{r ex-graph}
dehex::dh_graph(short)
```


Your IDE will likely show the RGB columns as their respective colours, thanks to [the {crayon} package](https://github.com/r-lib/crayon).

You can print the 12 primary, secondary and tertiary hues and assess the one with the most similar RGB distribution to yours:

```{r ex-hue}
dehex::dh_hue()
```

You can also view charts for the three broad lightness (L) categories. The higher the mean value, the lighter the colour is. By default, a marker is added to the chart to indicate the mean RGB value, which can help decide how light the colour is.

```{r ex-light}
dehex::dh_light()
```

You can also compare to the four broad saturation (S) categories. A greater range in RGB values means it's more saturated. By default, a bar is added to show the range of the RGB values.

```{r ex-sat}
dehex::dh_sat()
```

(Additional functionality to be added.)

## Code of Conduct

Please note that the {dehex} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
